---
title: "Steps to Create Repo"
format: html
---



## Steps to create repository

1. git clone https://github.com/brainworkup/brainworkup.github.io
1. cd brainworkup.github.io
1. echo "Hello World" > index.html
1. git add --all
1. git commit -m "Initial commit"
1. git push -u origin main
1. https://brainworkup.github.io

## add more to html

echo "My name is Joey" > index.html

## Put all code in the appendix
The key: the chunk option ref.label to reference other code chunks.

More info: https://yihui.org/en/2018/09/code-appendix/

You can move your code freely in an Rmd document using ref.label, without cut-and-paste.

9. Cache time-consuming code chunks
Use the chunk option cache = TRUE if a code chunk is time-consuming and the code doesn't change often.

11. Child documents
You can split your long documents into shorter ones, and include the shorter documents as child documents, e.g.,

```{r, child='analysis.Rmd', eval=FALSE}
```
```{r, child=c('one.Rmd', 'another.Rmd'), eval=FALSE}
```

Example: 15-conditional.Rmd
Choose a child document to include based on the P-value* of a regression coefficient.

13. Generate a plot and display it elsewhere
The key is fig.show = "hide", and the function knitr::fig_chunk().

16. Embed files in the HTML output
Sometimes you may want your clients or readers to be able to download certain files that you used in the Rmd docuemnt (e.g., a CSV data file).

Use the function xfun::embed_file().

This only works if the output file format is HTML (e.g., html_document,
ioslides_presentation, etc.).
